Counterexample to $1/T$ convergence of herding in infinite dimensions?

### 2013-12-04 nips-poster/nips-poster.tex
poster

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% BEGIN MOTIVATION BLOCK %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{block}{\large Motivation}
JS
\end{block}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% END MOTIVATION BLOCK %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% BEGIN APPLICATIONS BLOCK %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{block}{\large Special Cases and Applications}
JS?
\begin{columns}[t]
\begin{column}{0.45\linewidth}

\begin{block}{Subgradient descent}

\end{block}

\begin{block}{Conditional gradient descent}
\end{block}

\begin{block}{Thresholded gradient}
\end{block}

\end{column}
\begin{column}{0.45\linewidth}
\begin{block}{AHK low-rank SDP solver}
\end{block}

\begin{block}{$q$-herding}
\end{block}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% BEGIN MOTIVATION BLOCK %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{block}{\large Motivation}
Suppose we want to solve the following \emph{saddle point} problem:
\[ \min_u \max_{\theta} L(u, \theta), \]
where $L(u,\theta) = h(u) + \langle u, \theta \rangle - R(\theta)$. 
We assume that $h$ and $R$ are both convex and that $\langle \cdot, \cdot \rangle$ 
is an arbitrary bilinear map.

\textbf{Intuition:} $u$ is the ``primal'', $\theta$ is the ``dual''.

Tie-in with optimization: can recast as minimizing
\[ L(u) \eqdef \max_{\theta} L(u, \theta) = h(u) + R^*(u). \]

Here $R^*(u) \eqdef \max_{\theta} u^T\theta - R(\theta)$ is the 
\emph{Fenchel conjugate} of $\theta$.
\end{block}

\begin{block}{\large Fenchel conjugate properties}
Fenchel conjugates are a key component of \emph{Legendre-Fenchel duality} 
and also show up in mirror descent. It turns out that they will also be 
important for generalizing the Frank-Wolfe algorithm.

\textbf{Property 1:} If $R$ is convex then $R^{**} = R$.

\textbf{Property 2:} $\partial R^*(u) = \argmin_{\theta} u^T\theta - R(\theta)$.
\end{block}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% END MOTIVATION BLOCK %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% BEGIN APPLICATIONS BLOCK %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{block}{\large Special Cases and Applications}
Many particular algorithms can be cast into our framework.
\begin{columns}[t]
\begin{column}{0.45\linewidth}

\begin{block}{Conditional gradient (Frank-Wolfe)}
Let $h \equiv 0$. Then we have the updates
\begin{align*}
u_t &= \argmin_u u^T\theta_t \\
 &= \argmin_u u^T\partial R^*(\hat{u}_{t-1}),
\end{align*}
which is the Frank-Wolfe update for $R^*$.
\end{block}

\begin{block}{Thresholded Frank-Wolfe}
Suppose we want to minimize $\|u\|_1 + R^*(u)$. Then 
we can consider the following 
\emph{thresholded Frank-Wolfe algorithm}:
\begin{align*}
u_t &= \argmin_u \|u\|_1 + u^T\partial R^*(\hat{u}_{t-1}),
\end{align*}
which converges at the same rate as conditional gradient 
but also imposes sparsity.
\end{block}

\begin{block}{(Modified) subgradient}
Let $h(u) = \frac{\gamma}{2} \|u\|_2^2$. Then the primal version of the 
algorithm gives the updates:
\begin{align*}
u_{t+1} &= \argmin_{\theta} \frac{\gamma}{2}\|u\|_2^2 + u^T\hat{\theta}_t \\
 &= -\frac{1}{\gamma}\hat{\theta}_t \\
 &= -\frac{1}{\gamma} \frac{\sum_{s=1}^t \alpha_s \partial R^*(u_s)}{\sum_{s=1}^t \alpha_s}.
\end{align*}
\end{block}

\end{column}
\begin{column}{0.45\linewidth}
\begin{block}{AHK low-rank SDP solver}
Suppose we want to solve the SDP
\begin{align*}
\text{maximize }   & \Tr(A^TX) \\
\text{subject to } & X \succeq 0 \\
                  & X_{ii} \leq 1 \, \forall i
\end{align*}
Set \small{$L(X,y) = \Tr(A^TX) + \sum_{i=1}^n \left[y_i(X_{ii}-1) - \eta y_i\log y_i\right]$}.
Then updating $X$ is an eigenvalue problem and each update is rank $1$. This 
yields a variant of the Arora-Hazan-Kale fast SDP solver.
\end{block}

\begin{block}{$q$-herding}
The \emph{herding} algorithm finds a distribution $\mu$ over 
$\sX$ such that $\bE_{x \sim \mu}[\phi(x)] \approx \bar{\phi}$ 
for a given collection of moments $\phi$. It is equivalent to 
the dual version of our algorithm for
\[ L(\mu,\theta) = \bE_{x \sim \mu}\left[\theta^T[\phi(x)-\bar{\phi}]\right] - \frac{1}{2}\|\theta\|_2^2, \]
which hinges upon $\|\bar{\phi}\|_2$ existing. In infinite 
dimensions this may not be the case and we can instead use the 
\emph{$q$-herding} algorithm based on the updates
\[ L(\mu,\theta) = \bE_{x \sim \mu}\left[\theta^T[\phi(x)-\bar{\phi}]\right] - \frac{1}{q}\|\theta\|_q^q, \]
which only requires that $\|\bar{\phi}\|_p$ exists, where $\frac{1}{p} + \frac{1}{q} = 1$.
\end{block}
